Demo Manuscript

### 2019-03-06 src/manuscript/pandoc-frontiers-template/demo-manuscript.Rmd
Added quantity figure to demo manuscript
Created rudimentary and buggy Makefile

The annotation set for rice had a total of `r rice$n_c + rice$n_p + rice$n_f` annotations.

@@

>>>>

The annotation set for rice had a total of `r rice$n_c` annotations for cellular component.

@@

Now here is an actual figure I've been working on:

![Quantitiative lalala](../../../reports/figures/annotation_quantities.pdf)
